%!TEX root = gabarit-doctorat.tex
\chapter*{Foreword}         % ne pas numéroter
\phantomsection\addcontentsline{toc}{chapter}{Foreword} % inclure dans TdM

This thesis is submitted to the ``Faculté des études supérieures de l'Université Laval" to obtain the degree of Philosophiae Doctor of Science (Ph.D.). The current thesis is composed of six chapters. The first chapter is a literature review of maintaining the ``cold chain" in industry field, as well as cold approaches that are used nowadays in infrared thermography for Non-Destructive Testing \& Evaluation. This chapter concludes with the issue, hypothesis and objectives. In addition, several common data analyzing and processing methods, including modeling and simulation applied in whole research studies, are also presented and highlighted. Chapters two and three are presented in form of papers and describe the application of infrared thermography in the ``cold chain" and corresponding discussion. Chapters four and five are composed of manuscripts and describe the exploration of cold approaches in infrared thermography including several experimental results and discussions. Finally, in order to provide a closure on the results obtained in the current thesis, chapter six presents a general conclusions and proposed perspectives of the performed studies.

The first manuscript is entitled ``Mapping of the heat flux of an insulated small container by infrared thermography" and was presented at the 24th IIR International Congress of Refrigeration, in Yokohama, Japan. Authors: Paolo Bison, Alessandro Bortolin, Gianluca Cadelano, Giovanni Ferrarini, Lei Lei, Xavier Maldague, Stefano Rossi.

The second paper is entitled ``Panoramic View of the Heat Flux Inside an Insulated Vehicle by Infrared Thermography" and was first presented at an oral session of the 1st QIRT Asia Conference 2015 Mamallapuram, India. Then it was selected for publication in the Quantitative InfraRed Thermography Journal. Authors: Lei Lei, Alessandro Bortolin, Gianluca Cadelano, Giovanni Ferrarini, Stefano Rossi, Paolo Bison, Xavier Maldague. 

Then, the third article is entitled ``Detection of insulation flaws and thermal bridges in insulated truck box panels" and was first presented at an oral session of the 13th Quantitative InfraRed Thermography Conference 2016 at Gdańsk University of Technology in Poland. Then this paper was invited for publication in the Quantitative InfraRed Thermography Journal. Authors: Lei Lei, Alessandro Bortolin, Paolo Bison, Xavier Maldague.

The last manuscript is entitled ``Liquid nitrogen cooling in IR thermography applied to steel specimen" and it was accepted for publication in the Proceedings Volume 10214 of Thermosense: Thermal Infrared Applications XXXIX; 102140T (2017). Authors: Lei Lei, Giovanni Ferrarini, Alessandro Bortolin, Gianluca Cadelano, Paolo Bison, Xavier Maldague.

The main objectives of the present thesis are first to deploy the infrared thermography technique in the procedure of maintaining the ``cold food chain'', especially in insulated vehicles of ATP standards. The benefits of time-saving and the accuracy of the results in the determination of K-value could be applied for assessment at a commercial level. Then based on the previous favorable results, another objective is to explore cold approaches (such as compressed air, liquid nitrogen, etc.) in infrared thermography for Non-Destructive Testing \& Evaluation. The first part of this research was a cooperative project supported by the governments of Italy and Quebec (Ministère des Relations internationales et de la Francophonie) through the Joint Subcommittee Québec-Italy. Our collaborator, the Construction Technologies Institute of the Italian National Research Council (ITC-CNR), has made a significant contribution to this research. Three main experiments were performed at ITC-CNR, and Dr. Paolo Bison oversaw all steps of the work there.

For the exploration of cold approaches, the research supervisor, prof. Xavier Maldague collaborated in the set up and work planning of experiments, equipment and participated in the interpretation of the results and the revision of the manuscripts.

%\textbf{TO BE COMPLETED}


%Finally, the candidate has been invited to present the results of this thesis in a good management practices guide for pigs from farm to slaughter. This guide will be developed for use by the pork meat industry and the Canadian hog producers.
