%!TEX root = gabarit-doctorat.tex
\chapter*{Acknowledgements}         % ne pas numéroter
\phantomsection\addcontentsline{toc}{chapter}{Acknowledgements} % inclure dans TdM

Coming to study in Canada was the most important turning point of my life.

I would like to first give thanks my Ph.D supervisor, Xavier Maldague, who offered me the opportunity to come to Quebec and gave the chance to have three internships in Italy. I really appreciate his significant guidance, trustworthy support and advising encouragement during my Ph.D study. I want also to thank the member of thesis committee, Prof. Jean Dumoulin,  Prof. Pierre Servais and Dr. Stefano Sfarra, for spending part of their busy time on reading this manuscript and providing me beneficial comments and corrections.


Since one major part of this thesis is a joint project between the laboratory CNR-ITC of Padova in Italy and the Computer Vision and Systems Laboratory of University Laval, I’d like to express many thanks of gratitude to Dr. Paolo Bison and his research group—Alessandro Bortolin, Gianluca Cadelano, Giovanni Ferrarini, and the technical group—Stefano Rossi, Gianluca Cuccato, not only for all their kindness and help in preparation experiments and results discussions during my stay in Padova, but their suggestions and support of post-processing and redaction of conference papers as well. I really enjoyed the three stays in Italy, which made me learn more knowledge in research and certain applications in industry. In addition, the Italian foods have well refreshed my tastes.

On other hand, there was much help from the members of the Laboratory of Computer Vision and Systems. I thank all my colleges and friends from this laboratory. The union of discussing and spreading ideas, going to PEPS for sports, diner together at the weekend night, etc. all these have helped a lot to distract me out of some dull time during the research.

I would like also to thank all friends I've met in Quebec city. As known the winter here is much colder than one can imagine, but with them an home-feeling and warmhearted atmosphere has been created. 

Finally I'd like to express my gratitudes to my family, as they have always been a great source of mental energy for me. I have many reasons to say thank you to my parents, for their endless love, best wishes, unconditional support and so much confidence in me beyond my thought. I thank my wife Qilan for her patience, preparation of different delicious meals, and taking care of me considerately. I thank Steven, our one-year old son, for all the joy and happiness, lovely moments, invaluable experience that he has brought to us. 
